Section_8_Team1_Lab2_Report

### 2021-08-03 reports/Draft_Report.Rmd
added more to intro, code for ggaly.

---
title: "Section_8_Team1_Lab2_Report"
author: "Degnan, Rains, Wu"
date: "8/1/2021"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---

@@

We will analyze datasets pertaining to these variables for Texas counties and create three models to understand if causal relationships exist between distance traveled, population income, population density (rural or urban counties), and government regulations. Our hypothesis is that an there is a causal relationship between """

@@

```{r dataframe, echo=FALSE}
df <- read.csv('/home/jovyan/r_bridge/code/lab-2-lab2_section8_jal/data/interim/covid_trips_interim.csv')
head(df)

@@

To demonstrate the operationalization of the data, Tables 1 and 2 below display the original value counts from the dataset as well as how many values were removed as a part of filtering the dataset to remove all states except Texas. For the analysis, $$### responses were analyzed as shown in Table 1. Table 2 depicts the county type breakdown for rural or urban classification as well.

@@

step_num = c(1,2,3)

number_of_samples = c(nrow(df),
                      nrow(#newdf1),
                      nrow(#newdf2))                      
samples_removed = c(0,
                    nrow(df)-nrow(#newdf1),
                    nrow(#newdf1)-nrow(#newdf2))

reasoning = c("Original Dataset",
              "Removing XYZ",
              "Removing 123")

@@

# knitr::kable(accounting_df)
colnames(accounting_df) <- c('Step','Number of Samples','Samples Removed', 'Reason')
knitr::kable(accounting_df, caption="Accounting Table", align = "c")

# final_depRep_tab_df = dplyr::count(df, #df2, sort = TRUE)
# colnames(final_depRep_tab_df) <- c('County Type', 'Number of Samples')
# knitr::kable(final_depRep_tab_df, caption="Final Samples by County", align = "c")
```

@@

```{r EDA}
#Example Table
table1::label(df$total_pop) <- "TX County Population"
table1::label(df$sum_cases) <- "TX County Covid-19 Cases"

table1::table1(~total_pop + sum_cases | state, data = df)

@@

ggplot(df, aes(x=total_pop)) + geom_histogram(bins=100))
ggplot(df, aes(x=sum_cases)) + geom_histogram(bins=100)
ggplot(df, aes(x=sum_deaths)) + geom_histogram(bins=100) 
ggplot(df, aes(x=long_trip)) + geom_histogram(bins=100)

ggpairs(df, columns = 1:ncol(data), title = "EDA: Variable Correlation",  
  axisLabels = "show", columnLabels = colnames(data[, columns]))

@@

@@

>>>>

---
title: "Section_8_Team1_Lab2_Report"
author: "Degnan, Rains, Wu"
date: "8/5/2021"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---

@@

We will analyze datasets pertaining to these variables for Texas counties and create three models to understand if causal relationships exist between distance traveled, population income, population density (rural or urban counties), and government regulations. The outcome variable will be distance traveled. The predictor varialbes will be income, county type (rural or urban), and policy regulations around Covid-19. Our hypothesis is that an there is a causal relationship between these predictor variables and the outcome variable.

@@

```{r dataframe, echo=FALSE}
df <- read.csv('~/lab-2-lab2_section8_jal/data/interim/covid_trips_interim.csv')
head(df)

@@

To demonstrate the operationalization of the data, Tables 1 and 2 below display the original value counts from the dataset as well as how many values were removed as a part of filtering the dataset to remove all states except Texas. For the analysis, 230 responses were analyzed as shown in Table 1. Table 2 depicts the county type breakdown for rural or urban classification as well.

@@

step_num = c(1,2)

number_of_samples = c(nrow(df), #Need dataframe for all US
                      nrow(df))

samples_removed = c(0,
                    nrow(df)-nrow(df))

reasoning = c("Original Dataset",
              "Filtered for Texas Only")

@@

knitr::kable(accounting_df)
colnames(accounting_df) <- c('Step','Number of Samples','Samples Removed', 'Reason')
knitr::kable(accounting_df, caption="Accounting Table", align = "c")

#Need to create column category of rural vs urban - will create a summary table below with this
# final_tab_df = dplyr::count(df, df, sort = TRUE)
# colnames(final_tab_df) <- c('County Type', 'Number of Samples')
# knitr::kable(final_tab_df, caption="Final Samples by County", align = "c")
```

@@

```{r EDA}
#Example Table
table1::label(df$total_pop) <- "TX County Population"
table1::label(df$cases) <- "TX County Covid-19 Cases"

table1::table1(~total_pop + cases | state, data = df)

@@

ggplot(df, aes(x=total_pop)) + geom_histogram(bins=100)
ggplot(df, aes(x=cases)) + geom_histogram(bins=100)
ggplot(df, aes(x=deaths)) + geom_histogram(bins=100) 
ggplot(df, aes(x=long_trip)) + geom_histogram(bins=100)

df_test <- df

df_test <- df_test %>% mutate(County_Class = 
               case_when(df_test$total_pop <= 99999 ~ "Rural", 
                         df_test$total_pop >= 100000 ~ "Urban"))

# df_test$County_Rural <- ifelse(df_test$County_Class == "Rural", 1, 0) #will be useful for model
# df_test$County_Class <- as.factor(df_test$County_Class) #this turns

ggpairs(df_test, columns = 5:(ncol(df)-1), title = "EDA: Variable Correlation",  
  axisLabels = "show", aes(colour = County_Class, alpha = 0.4))

@@

<!-- Add language for model 2 and model 3 about CLM assumptions. -->

@@

Based upon the linear regression analysis above, it is observed that there may be a causal relationship between XX and YY. The hypothesis posed within the introduction is 'failed to be rejected/ rejected.' ....

For future analysis, it is recommended that Covid-19 policy adherence data per county be incorporated into the model to increase the accuracy. While the Govenor of Texas issued detailed protocols or mandates for the state of Texas, the degree to which each county (and thus the individual residents) complied would be useful data to have if such data were to exist.
